Design and Implementation of Probabilistic Programming Language Anglican

### 2017-02-08 paper/paper.tex
link to WebPPL distribution
added missing

We run this program for n equal to 10, 15, 20, and 25. Clojure
is consistently only twice as fast as Anglican
(Table~\ref{tbl:hanoi}); considering the amount of overhead
Anglican introduces, this is a good result.
\begin{table}
    \centering
    \begin{tabular}{r|r|r|r|r}
        {\bf n}  & {\bf 10} & {\bf 15} & {\bf 20} &{\bf 25} \\ \hline
        Clojure &  0.32 & 1.45 & 38.1  &  1245. \\ \hline
        Anglican & 0.63 & 3.00 & 75.9 & 2381. 
    \end{tabular}
    \caption{Towers of Hanoi. Running times, in
    seconds, of Clojure and Anglican, averaged over 100 runs.
    Clojure is only twice as fast as Anglican.}
    \label{tbl:hanoi}
\end{table}

The other comparison must be made between Anglican and another
probabilistic programming environment. WebPPL~\cite{GS15} is
similar to Anglican in expressivity.  WebPPL runs on top of
\href{http://v8project.blogspot.com/}{V8}, a high performance
JavaScript engine featuring a native compiler.
Table~\ref{tbl:webppl} shows results for two models from WebPPL
distribution, \textit{LDA} and
\textit{Logistic regression}. For
comparison, we re-implemented the models in Anglican, as close
as possible to the WebPPL implementations, and run the same
inference algorithm (called MCMC in WebPPL, LMH in Anglican)
with the same number of iterations. Anglican outperforms WebPPL
on both models. This can be attributed both to a better
transformed representation of probabilistic programs and to more
efficient architecture of the inference engine.
\begin{table}
    \centering
    \begin{tabular}{r|c|c}
        {\bf model}  & {\bf LDA} & {\bf Logistic regression} \\ \hline
        Anglican & 22. & 4.8 \\ \hline
        WebPPL & 31. & 9.4
    \end{tabular}

>>>>

We run this program for \texttt{n} equal to 10, 15, 20, and 25. Clojure
is consistently only twice as fast as Anglican
(Table~\ref{tbl:hanoi}); considering the amount of overhead
Anglican introduces, this is a good result.
\begin{table}
    \centering
    \begin{tabular}{r|r|r|r|r}
        {\bf n}  & {\bf 10} & {\bf 15} & {\bf 20} &{\bf 25} \\ \hline
        Clojure &  0.32 & 1.45 & 38.1  &  1245. \\ \hline
        Anglican & 0.63 & 3.00 & 75.9 & 2381. 
    \end{tabular}
    \caption{Towers of Hanoi. Running times, in
    seconds, of Clojure and Anglican, averaged over 100 runs.
    Clojure is only twice as fast as Anglican.}
    \label{tbl:hanoi}
\end{table}

The other comparison must be made between Anglican and another
probabilistic programming environment. WebPPL~\cite{GS15} is
similar to Anglican in expressivity.  WebPPL runs on top of
\href{http://v8project.blogspot.com/}{V8}, a high performance
JavaScript engine featuring a native compiler.
Table~\ref{tbl:webppl} shows results for two models from
\href{https://github.com/probmods/webppl}{WebPPL
distribution}, \textit{LDA} and
\textit{Logistic regression}. For
comparison, we re-implemented the models in Anglican, as close
as possible to the WebPPL implementations, and run the same
inference algorithm (called MCMC in WebPPL, LMH in Anglican)
with the same number of iterations. Anglican outperforms WebPPL
on both models. This can be attributed both to a better
transformed representation of probabilistic programs and to more
efficient architecture of the inference engine.
\begin{table}
    \centering
    \begin{tabular}{r|c|c}
        {\bf model}  & {\bf LDA} & {\bf Logistic regression} \\ \hline
        Anglican & 22. & 4.8 \\ \hline
        WebPPL & 31. & 9.4
    \end{tabular}
